Merits of hypermedia systems

### 2013-06-06 dagstuhl-2013/position.tex
Some details about hypermedia
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@585 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}

@@

\section{Hypermedia RDF}

In \cite{kjernsmo_lapis_2012}, examined some practical implications of
the HATEOAS constraint of the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5., and in that
light argued why hypermedia RDF is a practical necessity.

Mike Amundsen defines hypermedia types\cite{hypermediatypes} as 
\begin{quote}
Hypermedia Types are MIME media types that contain native
hyper-linking semantics that induce application flow. For example,
HTML is a hypermedia type; XML is not.
\end{quote}

We continued to derive a powerful hypermedia type based on RDF within
a classification suggested by Mike Amundsen. Since this publication, I
have also noted that the embedded links factor can be achieved by
using \texttt{data} URIs, thus satisfying all but one of the factors
proposed by Mike Amundsen.

Further, we noted that other interesting factors is the
self-description, which is a important characteristic of the RDF
model, and other voiced other minor concerns.

To bring forward a concrete example of how to make a serialized RDF
graph into a hypermedia type, we suggest adding some triples to every
resource (where prefixes are omitted for brevity):

\begin{verbatim}
<> hm:canBe hm:mergedInto, hm:replaced, hm:deleted ;
   hm:inCollection <../> ;
   void:inDataset [ void:sparqlEndpoint </sparql> . ] .
\end{verbatim}

\bibliographystyle{plain}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{federation,webarch,vocabs,specs,hypermedia,egne,selectivity}

\end{document}
